\addcontentsline{toc}{part}{Acknowledgments}
\chapter*{Acknowledgments}

I am very grateful to Dr. Frank Ohme and Dr. Wolfgang Kastaun for the time they spent helping me learn about gravitational wave astrophysics and get through all the challenges I faced while producing the results I presented in this thesis. I would also like to thank Dr. Jairo Alonso Ayala Molina and Dr. Domenico Giulini since their lectures and guidance gave me the courage to take this research path.

From the deepest place of my heart, I want to thank Ing. Katherine Vanessa Insuasty Martinez for being by my side all these years. Her support and love helped me stay happy and focused during the loneliest days away from her and my family.

No hay palabras suficientes para expresar lo importantes que han sido mis padres desde mi niñez hasta el dia de hoy. Es gracias a ellos que sigo disfrutando de hacer preguntas que un niño de 5 años haría y dedico mi tiempo a intentar responderlas usando habilidades que no tendría de no ser por ellos. Ellos siempre me apoyaron y animaron a seguir mis dos sueños: ser tenista y convertirme en astrofísico. Como suele decir mi madre "un niño es una hoja en blanco que un padre escribe durante varios años", yo me siento feliz de ser esa hoja en blanco que Luz Elena y William decidieron empezar a escribir hace un  mas de 25 años.

Quiero agradecer y recordar a mi tia Tránsito Gómez Casallas quien no está más con nosotros y fue la primera persona de mi familia que me reconoció como un excelente ingeniero fisico.

I want to thank my friends Marius Schulz, Angela Borchers, Rahul Drukhunde, Max Melching, Swapnil Singh, Dr.~Cecilio Garcia Quiros, Marlin Schäfer, Dr.~Krishnendu Naderi Varium, and Dr.~Pierre Mourier for making my stay in Hannover much more than an incredible academic experience. I had such a great time!

I want to acknowledge Max Planck Gesellschaft for the support and the AEI Hannover for providing the computational infrastructure and a great scientific atmosphere.
